%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {LifeSG app and BookingSG platform} % Project description
    {Government Digital Services App - GovTech Singapore} % Project title & company name
    {PALO IT, Hong Kong} % Location
    {Jun. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built reusable components to deliver new app features to enhance user experience of using LifeSG app.}
        \item {Established APIs for data writing, fetching and sorting.}
        \item {\textit{React-native, React Hooks, Redux, Redux Thunk, Typescript, Jest}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Global sourcing and quotation platform} % Project description
    {Sales Quotation System - Concept 4 Hong Kong} % Project title & company name
    {PALO IT, Hong Kong} % Location
    {Aug. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the prioritized application features in product backlog using MVP approach.}
        \item {Refactored old code to maintain sustainability of the application and improve system efficiency.}
        \item {\textit{React, Redux Saga, Axios, Sequelize, Node.js, Express.js, Docker, SQL}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Merchandising system to facilitate sourcing and negotiation process} % Project description
    {Selection Price List - Lidl Hong Kong} % Project title & company name
    {PALO IT, Hong Kong} % Location
    {Mar. 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivered major features and handled defects to meet the client's needs in agile development approach.}
        \item {Collaborated and facilitated sprint ceremonies (sprint planning, demo and retrospective).}
        \item {\textit{Javascript, Material UI, Ant Design, Oracle SQL Developer}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
